\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Added iptables graphs

\section{Statistics}
\label{Statistics}
In this section we will discuss the statistical data that have been gathered from our logfiles.

>>>>

\section{Statistics}
\label{Statistics}
In this section we will discuss the statistical data that have been gathered from our logfiles. 
The logged connection attempts have been processed to group them by the IP address' originating country through the use of WHOIS directory service information.
It is worthwhile noting that a significant number of connecting hosts could not be referenced to RWHOIS information.
Also note that these graphs display all logged connection attempts rather than successful connections, giving us a general view of which ports attract attention.

For clarity we have chosen to graph only the 10 most active originating countries, and make use of a logarithmic scale to represent the spectrum of port numbers.
The labels on the \(y\)-axis were chosen based on the most frequently accessed ports, with some selected labels removed to avoid clutter.

\includegraphics[width=1.7\textwidth,angle=-90]{tcp}

\includegraphics[width=1.7\textwidth,angle=-90]{udp}
